bayes_droplet

### 2021-08-20 analysis/bayes_droplet.Rmd
nb

```{r}
emm %>% 
  mutate(response = round(response, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, response), 
             y = response, 
             color = trt, 
             shape = type)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
                 position = position_dodge2(width = 0.4), 
                 size = 1.3, alpha = 0.5) +
  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
  geom_jitter(data = droplet1,
                position = position_dodge2(width = 0.4),
              mapping = aes(color = trt, shape = type), alpha = 0.1, size = 2) +
  coord_flip() +
  geom_text_repel(aes(label = response, 
                         x = trt, color = trt, shape = type),
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
  labs(x = NULL, y = "Droplet size (µm)", color = NULL, shape = NULL) +
  scale_color_viridis_d(option = "H") +
  scale_y_continuous(limits = c(0, 1500), breaks = seq(0, 1500, 300)) +
  scale_shape_manual(values = c(8,9,10)) +
  theme_few() + 
  theme(legend.position = c(0.85, 0.2),
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) +
  guides(color = "none") -> fig1

@@

```{r}
em4 %>% 
  mutate(response = round(response, 2)) %>% 
  ggplot(aes(x = fct_reorder(trt, response), y = response, color = trt)) +
  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
                 position = position_dodge2(width = 0.4), size = 1.3) +
  coord_flip() +
  geom_jitter(data = droplet2,
              mapping = aes(color = trt), alpha = 0.1, size = 2) +
  geom_text_repel(aes(label = response, 
                         x = trt),
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
#  annotate("text", x = 5, y = 0.1, label = "There are differences \namong all pairwise trt  \ncomparisons (P <.0001) \nin figures A, B and C", size = 9, hjust = 0, lineheight = 0.3,
#           color = 1, fontface = "italic") +
  labs(x = NULL, y = "Relative span", color = NULL) +
  scale_color_viridis_d(option = "H") +
  scale_y_continuous(limits = c(0, 1.2), breaks = seq(0, 1.2, 0.2)) +
  theme_few() + 
  theme(legend.position = "none",
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) -> fig2
```

@@

```{r}
em5 %>% 
  mutate(response = round(response, 4)) %>% 
  ggplot(aes(x = fct_reorder(trt, response*100), y = response*100, color = trt)) +
  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
  geom_linerange(aes(ymin = lower.HPD*100, ymax = upper.HPD*100),
                 position = position_dodge2(width = 0.4), size = 1.3) +
  coord_flip() +
  geom_jitter(data = droplet2, 
              mapping = aes(color = trt), alpha = 0.1, size = 2) +
  geom_text_repel(aes(label = response*100, 
                         x = trt),
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
#  annotate("text", x = 2, y = 3, label = "There are differences \namong all pairwise trt \ncomparisons (P <.0001)", size = 9, hjust = 0, lineheight = 0.3,
#           color = 1, fontface = "italic") +
  labs(x = NULL, y = "% driftable fines < 200 µm", color = NULL) +
  scale_color_viridis_d(option = "H") +
  scale_y_continuous(limits = c(0, 10), breaks = seq(0, 10, 2)) +
  theme_few() + 
  theme(legend.position = "none",
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) -> fig3
```

>>>>

```{r}
emm %>% 
  mutate(response = round(response, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, response), 
             y = response, 
             color = trt, 
             shape = type)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
                 position = position_dodge2(width = 0.4), 
                 size = 1.3, alpha = 0.5) +
  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
  geom_jitter(data = droplet1,
                position = position_dodge2(width = 0.4),
              mapping = aes(color = trt, shape = type), alpha = 0.1, size = 2) +
  coord_flip() +
  geom_text_repel(aes(label = response, 
                         x = trt, color = trt, shape = type),
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
  labs(x = NULL, y = "Droplet size (µm)", color = NULL, shape = NULL) +
  scale_color_viridis_d(option = "H") +
  scale_y_continuous(limits = c(0, 1500), breaks = seq(0, 1500, 300)) +
  scale_shape_manual(values = c(8,9,10)) +
  theme_few() + 
  theme(legend.position = c(0.85, 0.2),
        legend.text = element_markdown(size = 25),
        legend.margin = margin(0, 0, 0, 0),
        legend.spacing.x = unit(0, "mm"),
        legend.spacing.y = unit(0, "mm"),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) +
  guides(color = "none") -> fig1

@@

```{r}
em4 %>% 
  mutate(response = round(response, 2)) %>% 
  ggplot(aes(x = fct_reorder(trt, response), y = response, color = trt)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
                 position = position_dodge2(width = 0.4), 
                 size = 1.3, alpha = 0.5) +
  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
  coord_flip() +
  geom_jitter(data = droplet2,
              mapping = aes(color = trt), alpha = 0.1, size = 2) +
  geom_text_repel(aes(label = response, 
                         x = trt),
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
#  annotate("text", x = 5, y = 0.1, label = "There are differences \namong all pairwise trt  \ncomparisons (P <.0001) \nin figures A, B and C", size = 9, hjust = 0, lineheight = 0.3,
#           color = 1, fontface = "italic") +
  labs(x = NULL, y = "Relative span", color = NULL) +
  scale_color_viridis_d(option = "H") +
  scale_y_continuous(limits = c(0, 1.2), breaks = seq(0, 1.2, 0.2)) +
  theme_few() + 
  theme(legend.position = "none",
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) -> fig2
```

@@

```{r}
em5 %>% 
  mutate(response = round(response, 4)) %>% 
  ggplot(aes(x = fct_reorder(trt, response*100), y = response*100, color = trt)) +
  geom_linerange(aes(ymin = lower.HPD*100, ymax = upper.HPD*100),
                 position = position_dodge2(width = 0.4), 
                 size = 1.3, alpha = 0.5) +
  geom_point(size = 2, position = position_dodge2(width = 0.4)) +
  coord_flip() +
  geom_jitter(data = droplet2, 
              mapping = aes(color = trt), alpha = 0.1, size = 2) +
  geom_text_repel(aes(label = response*100, 
                         x = trt),
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
#  annotate("text", x = 2, y = 3, label = "There are differences \namong all pairwise trt \ncomparisons (P <.0001)", size = 9, hjust = 0, lineheight = 0.3,
#           color = 1, fontface = "italic") +
  labs(x = NULL, y = "% driftable fines < 200 µm", color = NULL) +
  scale_color_viridis_d(option = "H") +
  scale_y_continuous(limits = c(0, 10), breaks = seq(0, 10, 2)) +
  theme_few() + 
  theme(legend.position = "none",
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) -> fig3
```
